\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}

\title{ORIE 5270 Project Summary\\Generative Retrieval for Multi-Destination Trip Prediction}
\author{Althea Lam}
\date{\today}

\begin{document}
\maketitle
\onehalfspacing

\section*{Project Goal}
The goal is to predict the \textbf{next destination city} from an incomplete multi-city trip.  
Evaluation metric: \textbf{Accuracy@4} (whether the true city appears in top-4 predictions).

\section*{Dataset and Setup}
\begin{itemize}[leftmargin=1.5em]
    \item Dataset: Booking.com Multi-Destination Trips (WSDM WebTour 2021).
    \item Train: 1,166,835 booking rows.
    \item Test: 378,667 booking rows (70,662 trips to complete).
    \item Each trip is built by sorting by check-in time and grouping by \texttt{utrip\_id}.
\end{itemize}

\section*{What I Implemented}
I compared three pipelines under both Transformer and GRU backbones:
\begin{enumerate}[leftmargin=1.5em]
    \item \textbf{Embedding pipeline}: direct next-city prediction from city token prefixes.
    \item \textbf{RQVAE pipeline}: predict next semantic code pair, then decode to city candidates.
    \item \textbf{RQKMeans pipeline}: residual k-means codebook + next code-pair prediction + decoding.
\end{enumerate}

\textbf{Feature engineering used across runs}:
\begin{itemize}[leftmargin=1.5em]
    \item sequence features (city prefix),
    \item temporal features (month, stay duration),
    \item trip-structure features (trip length, repetition statistics),
    \item geography features (hotel-country transitions, cross-border stats),
    \item user/context features (booker country, device class, affiliate).
\end{itemize}

\section*{Main Results}
\begin{table}[h]
\centering
\begin{tabular}{lcc}
\toprule
\textbf{Pipeline} & \textbf{Transformer Best} & \textbf{GRU Best} \\
\midrule
Embedding (direct city token) & 0.4871 & \textbf{0.4891} \\
RQ-VAE (code pair decoding) & 0.3384 & 0.3487 \\
RQKMeans (code pair decoding) & 0.3066 & 0.3291 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Key takeaway}: direct city-token prediction is currently the strongest approach in this project setting.

\section*{Most Important Findings}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Model family}: Embedding route consistently outperformed code-based routes.
    \item \textbf{Training strategy}: multi-step training usually improved performance, but increased runtime.
    \item \textbf{Implementation detail}: fixing hidden-state extraction gave significant gains.
    \item \textbf{Pooling}: Transformer \texttt{last}/\texttt{mean} worked much better than \texttt{cls}.
    \item \textbf{Features}: geography and trip-structure features provided measurable improvement.
\end{itemize}

\section*{Engineering Notes}
\begin{itemize}[leftmargin=1.5em]
    \item Code is modularized into \texttt{src/features}, \texttt{src/models}, \texttt{src/training}, \texttt{src/datasets}, and runnable \texttt{scripts/}.
    \item A major data-quality fix was applied: context features are now prefix-aligned to avoid future-information leakage.
\end{itemize}

\section*{Limitations}
\begin{itemize}[leftmargin=1.5em]
    \item Results are based on repository-best runs across multiple feature/architecture revisions.
    \item RQ-based methods may need stronger decoding/reranking to close the gap.
    \item Not all hyperparameter combinations were exhaustively searched.
\end{itemize}

\section*{Next Steps}
\begin{itemize}[leftmargin=1.5em]
    \item add validation-based early stopping and scheduler tuning,
    \item improve RQ code-to-city decoding and reranking,
    \item test lightweight ensemble of embedding + RQ pipelines.
\end{itemize}

\section*{Selected References}
\begin{itemize}[leftmargin=1.5em]
    \item Booking.com Multi-Destination Trips Dataset: \url{https://github.com/bookingcom/ml-dataset-mdt}
    \item van den Oord et al., ``Neural Discrete Representation Learning'' (NeurIPS 2017).
    \item Jegou et al., ``Product Quantization for Nearest Neighbor Search'' (TPAMI 2011).
    \item Sun et al., ``BERT4Rec'' (CIKM 2019).
    \item Rajput et al., ``Recommender Systems with Generative Retrieval'' (NeurIPS 2023).
\end{itemize}

\end{document}
